An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-03-26 poly-embed-journal/poly-embed-journal.tex
Minor tweaks; hopefully no conflicts

%\raf{MOVED FROM SEC 2; maybe incorporate?}
%Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
%We now formalize this procedure.
%
\jessie{ TODO Items 01 Mar 2021
	\begin{itemize}
		\item \sout{Reorg sections: \S 3 (Embeddings, matching risks, etc.), \S 5 (Calibrated link), Examples, \S 4 (Polyhedral losses: I.E. implies consistency) OR Main results (w/o proof), Examples, \S 3, \S 5, \S 4}
		\item \sout{Flesh out and expand on Ordered Partition Example}
		\item add paragraph of discussion on the requirements of polyhedral losses
		\item Check proof and statement of Theorem~\ref{thm:poly-ie-implies-consistent} - Jessie, 17 Mar 21: took a look to brush up; Theorem~\ref{thm:ie-iff-embeds-refinement} can use a look too.
		\item Try to make section~\ref{sec:poly-loss-embed} self-contained, moving up results from appendix 
		\begin{itemize}
		\item \sout{for now, move everything up except PDs}
		\item see if you can isolate what exactly we need from PDs and state it as a new lemma (which is just about Bayes risks)
		\item rethink proofs of Prop 1 and 2, see if we resolve the redundancy
		\end{itemize}
		\item Make Cor 1 a Theorem: "For L polyhedral, ell discrete, L ind elic prop[ell] <==> L consistent wrt ell"
\end{itemize}
TODO Items summer 2020
	\begin{itemize}
		\item Formalize reverse implication proof of Proposition 1 with projections into the affine hull and back
		\item Mention how our focus on polyhedral risks and general links extends DKR Section 3.1 (probably after Prop 1)
		\item Replace Proposition 2 with Lemma 7?
		\item Theorem 2: move from n-dimensional construction to n-1 dimensional construction (or add n-1 dim construction in appendix if it gets too hairy?)
	\end{itemize}}

@@

    \btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.  It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
  In what follows, we implicitly work in the affine hull of $\simplex$ by taking an appropriate invertible linear projection $A : \reals^n_+ \to \reals^{n-1}_+$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the interior of $\simplex$.
  (For intuition, one can consider the relative interiors in $\reals^n_+$, but we need to consider interiors in order to apply previous results.)
  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
%  Moreover, consider the linear transformation $P: \ell \mapsto [\mathbb{I}_{n-1}, \vec 0] \risk{\ell}$ projecting $\risk{\ell}$ down to $n-1$ dimensions.
  The projection of its epigraph $E_{\ell}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional (in $n-1$ dimensions) and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.

>>>>

%\raf{MOVED FROM SEC 2; maybe incorporate?}
%Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
%We now formalize this procedure.
%
\jessie{ TODO Items 01 Mar 2021
	\begin{itemize}
		\item \sout{Reorg sections: \S 3 (Embeddings, matching risks, etc.), \S 5 (Calibrated link), Examples, \S 4 (Polyhedral losses: I.E. implies consistency) OR Main results (w/o proof), Examples, \S 3, \S 5, \S 4}
		\item \sout{Flesh out and expand on Ordered Partition Example}
		\item add paragraph of discussion on the requirements of polyhedral losses
		\item Check proof and statement of Theorem~\ref{thm:poly-ie-implies-consistent} - Jessie, 17 Mar 21: took a look to brush up; Theorem~\ref{thm:ie-iff-embeds-refinement} can use a look too.
		\item Try to make section~\ref{sec:poly-loss-embed} self-contained, moving up results from appendix 
		\begin{itemize}
		\item \sout{for now, move everything up except PDs}
		\item see if you can isolate what exactly we need from PDs and state it as a new lemma (which is just about Bayes risks)
		\item rethink proofs of Prop 1 and 2, see if we resolve the redundancy
		\end{itemize}
		\item Make Cor 1 a Theorem: "For L polyhedral, ell discrete, L ind elic prop[ell] <==> L consistent wrt ell"
\end{itemize}
TODO Items summer 2020
	\begin{itemize}
		\item Formalize reverse implication proof of Proposition 1 with projections into the affine hull and back
		\item Mention how our focus on polyhedral risks and general links extends DKR Section 3.1 (probably after Prop 1)
		\item Replace Proposition 2 with Lemma 7?
		\item Theorem~\ref{thm:discrete-loss-poly-embeddable}: move from n-dimensional construction to n-1 dimensional construction (or add n-1 dim construction in appendix if it gets too hairy?)
	\end{itemize}}

@@

    \btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.  It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
  In what follows, we implicitly work in the affine hull of $\simplex$ by taking an appropriate invertible linear projection $A : \reals^n_+ \to \reals^{n-1}_+$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the interior of $\simplex$.
  (For intuition, one can consider the relative interiors in $\reals^n_+$, but we need to consider interiors in order to apply previous results.)
  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
%  Moreover, consider the linear transformation $P: \ell \mapsto [\mathbb{I}_{n-1}, \vec 0] \risk{\ell}$ projecting $\risk{\ell}$ down to $n-1$ dimensions.
  The projection of its epigraph $E_{\ell}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional (in $n-1$ dimensions) and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$. \jessiet{Don't need Theorem 1; can use Lemma~\ref{lem:finite-full-dim} instead.}
